Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-12-27 article.tex
More text

Conversely, managed languages such as Java and C# typically don't depend on the LLVM toolchain directly, research projects that attempt to compile associated VM bytecode to a native platform using LLVM.

@@

@@

\begin{table}[!h]

@@

\caption{\label{demo-table}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\caption{\label{demo-table}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\caption{\label{demo-table}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\caption{\label{demo-table}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\subsubsection{\lstinline!benches/sieven.ll!}
\begin{table}[!h]
\begin{center}
\begin{NiceTabular}{|c|cccccccc|}
\hline
n & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear & greedy 12 & greedy 0 \\
\hline
128 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.98451x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.98378x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.98295x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00304x& \cellcolor[rgb]{0.8154296875,0.9990234375,0.75} 1.26346x& \cellcolor[rgb]{0.8125,0.9990234375,0.75} 1.25285x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24850x\\
256 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01514x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00375x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.98807x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00262x& \cellcolor[rgb]{0.869140625,0.9990234375,0.75} 1.47906x& \cellcolor[rgb]{0.8876953125,0.9990234375,0.75} 1.55358x& \cellcolor[rgb]{0.8857421875,0.9990234375,0.75} 1.54756x\\
512 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00899x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03156x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03499x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01201x& \cellcolor[rgb]{0.9990234375,0.998046875,0.75} 2.00339x& \cellcolor[rgb]{0.9990234375,0.9951171875,0.75} 2.09435x& \cellcolor[rgb]{0.9990234375,0.994140625,0.75} 2.14397x\\
1024 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.03016x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02839x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01247x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.03097x& \cellcolor[rgb]{0.9990234375,0.97265625,0.75} 2.84545x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.07906x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.07390x\\
2048 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03732x& \cellcolor[rgb]{0.7607421875,0.9990234375,0.75} 1.04387x& \cellcolor[rgb]{0.7802734375,0.9990234375,0.75} 1.12328x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04998x& \cellcolor[rgb]{0.9990234375,0.9287109375,0.75} 4.24679x& \cellcolor[rgb]{0.9990234375,0.919921875,0.75} 4.52175x& \cellcolor[rgb]{0.9990234375,0.91796875,0.75} 4.60346x\\
4096 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7646484375,0.9990234375,0.75} 1.05883x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12849x& \cellcolor[rgb]{0.7626953125,0.9990234375,0.75} 1.05254x& \cellcolor[rgb]{0.775390625,0.9990234375,0.75} 1.10378x& \cellcolor[rgb]{0.9990234375,0.8720703125,0.75} 6.05831x& \cellcolor[rgb]{0.9990234375,0.8583984375,0.75} 6.50294x& \cellcolor[rgb]{0.9990234375,0.8544921875,0.75} 6.61920x\\
8192 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7724609375,0.9990234375,0.75} 1.09357x& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.24057x& \cellcolor[rgb]{0.7744140625,0.9990234375,0.75} 1.10146x& \cellcolor[rgb]{0.7783203125,0.9990234375,0.75} 1.11378x& \cellcolor[rgb]{0.9990234375,0.80859375,0.75} 8.09302x& \cellcolor[rgb]{0.9990234375,0.7900390625,0.75} 8.69270x& \cellcolor[rgb]{0.9990234375,0.783203125,0.75} 8.92530x\\
16384 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10882x& \cellcolor[rgb]{0.7822265625,0.9990234375,0.75} 1.13274x& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10937x& \cellcolor[rgb]{0.78515625,0.9990234375,0.75} 1.14416x& \cellcolor[rgb]{0.9990234375,0.7548828125,0.75} 9.84245x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.69728x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.80864x\\
\hline
\end{NiceTabular}
\caption{\label{demo-table}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}
\end{center}
\end{table}

@@

\begin{NiceTabular}{|c|cccccccc|}
\hline
n & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear & greedy 12 & greedy 0 \\
\hline
100 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9619140625,0.75} 3.17253x& \cellcolor[rgb]{0.9990234375,0.9560546875,0.75} 3.35873x& \cellcolor[rgb]{0.9990234375,0.9619140625,0.75} 3.17637x& \cellcolor[rgb]{0.9990234375,0.9560546875,0.75} 3.37014x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.50758x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.44391x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.61921x\\
1000 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9189453125,0.75} 4.54197x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.83710x& \cellcolor[rgb]{0.9990234375,0.9189453125,0.75} 4.54593x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.83359x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.35583x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.26454x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.56475x\\
10000 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80821x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.11478x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80648x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.12019x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.50659x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.41428x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.72138x\\
\hline
\end{NiceTabular}

>>>>

Conversely, managed languages such as Java and C\# typically don't depend on the LLVM toolchain directly, research projects that attempt to compile associated VM bytecode to a native platform using LLVM (\cite{dotnet}). Meanwhile interpreted languages like JavaScript eagerly attempt use LLVM for \textit{just-in-time} (JIT) compilation % FIXME: this is not true at all lol

@@

\subsection{Static Single-Assignment form}
In compiler backends, \textit{Static Single-Assignment} (SSA) form is a property that applies to some IR, including LLVM.
It is a way of representing a program in such a way that each variable is assigned only once throughout
the scope of the function. Each use of the variable after definition then refers to the value  of that initial assignment.
%In other words, every variable is assigned a unique version number for each assignment, and these versions are used consistently throughout the program.

@@

\begin{table}[!ht]

@@

\caption{\label{tab:dumb-fib}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\caption{\label{tab:dumb-fib-greedy}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\caption{\label{tab:factori32}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\caption{\label{tab:factori64-table}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\subsubsection{\lstinline!benches/sieven.ll!}
\begin{table}[!ht]
arg(s) & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear & greedy 12 & greedy 0 \\
128 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 159130& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00777x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00293x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00644x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01562x& \cellcolor[rgb]{0.8173828125,0.9990234375,0.75} 1.27104x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29856x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29894x\\
256 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 163800& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00726x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01200x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00852x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01440x& \cellcolor[rgb]{0.8818359375,0.9990234375,0.75} 1.53225x& \cellcolor[rgb]{0.89453125,0.9990234375,0.75} 1.58048x& \cellcolor[rgb]{0.8974609375,0.9990234375,0.75} 1.59431x\\
512 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 172096& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01902x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02488x& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01789x& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01876x& \cellcolor[rgb]{0.9990234375,0.9970703125,0.75} 2.03762x& \cellcolor[rgb]{0.9990234375,0.994140625,0.75} 2.13731x& \cellcolor[rgb]{0.9990234375,0.9931640625,0.75} 2.15792x\\
1024 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 188591& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03687x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03706x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02964x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03689x& \cellcolor[rgb]{0.9990234375,0.9697265625,0.75} 2.93413x& \cellcolor[rgb]{0.9990234375,0.9638671875,0.75} 3.09867x& \cellcolor[rgb]{0.9990234375,0.962890625,0.75} 3.15326x\\
2048 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 221875& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04971x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06586x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04806x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06306x& \cellcolor[rgb]{0.9990234375,0.92578125,0.75} 4.34620x& \cellcolor[rgb]{0.9990234375,0.916015625,0.75} 4.64145x& \cellcolor[rgb]{0.9990234375,0.9140625,0.75} 4.72466x\\
4096 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 288132& \cellcolor[rgb]{0.771484375,0.9990234375,0.75} 1.08649x& \cellcolor[rgb]{0.7744140625,0.9990234375,0.75} 1.09864x& \cellcolor[rgb]{0.76953125,0.9990234375,0.75} 1.08082x& \cellcolor[rgb]{0.7744140625,0.9990234375,0.75} 1.10033x& \cellcolor[rgb]{0.9990234375,0.8662109375,0.75} 6.25886x& \cellcolor[rgb]{0.9990234375,0.8525390625,0.75} 6.69614x& \cellcolor[rgb]{0.9990234375,0.84765625,0.75} 6.84597x\\
8192 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 424179& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10601x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12721x& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10683x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12700x& \cellcolor[rgb]{0.9990234375,0.8037109375,0.75} 8.26470x& \cellcolor[rgb]{0.9990234375,0.78515625,0.75} 8.85856x& \cellcolor[rgb]{0.9990234375,0.7783203125,0.75} 9.07318x\\
16384 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 697378& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12603x& \cellcolor[rgb]{0.787109375,0.9990234375,0.75} 1.15191x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12581x& \cellcolor[rgb]{0.787109375,0.9990234375,0.75} 1.15269x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.00521x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.73828x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.98249x\\
\caption{\label{demo-table}Benchmark of \texttt{benches/sieven.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

@@

\subsubsection{\lstinline!benches/sha256.ll!}
\begin{NiceTabular}{|c|cccccccc|}
\hline
n & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear & greedy 12 & greedy 0 \\
\hline
100 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9619140625,0.75} 3.17253x& \cellcolor[rgb]{0.9990234375,0.9560546875,0.75} 3.35873x& \cellcolor[rgb]{0.9990234375,0.9619140625,0.75} 3.17637x& \cellcolor[rgb]{0.9990234375,0.9560546875,0.75} 3.37014x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.50758x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.44391x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 19.61921x\\
1000 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9189453125,0.75} 4.54197x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.83710x& \cellcolor[rgb]{0.9990234375,0.9189453125,0.75} 4.54593x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.83359x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.35583x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.26454x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 31.56475x\\
10000 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80821x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.11478x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.80648x& \cellcolor[rgb]{0.9990234375,0.9013671875,0.75} 5.12019x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.50659x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.41428x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 33.72138x\\
\hline
\end{NiceTabular}
